### 2015-07-07 doc/manual/inputParameters.tex
Added ExBDerivativeScheme option for upwinding

\param{magneticDriftScheme}
{integer}
{0}
{Whenever \parlink{RHSMode} == 1.}
{This variable controls the poloidal and magnetic drifts, and does not affect the radial magnetic drift.
THIS FUNCTIONALITY IS WORK IN PROGRESS, AND RESULTS ARE BUGGY WHEN THIS VARIABLE IS NONZERO.\\

@@

>>>>

\param{magneticDriftScheme}
{integer}
{0}
{Whenever \parlink{RHSMode} == 1.}
{This variable controls the poloidal and magnetic drifts, and does not affect the radial magnetic drift.\\

@@

\param{ExBDerivativeScheme}
{integer}
{0}
{Whenever the radial electric field is nonzero}
{Options for controlling upwinding of the $\vect{E}\times\vect{B}$ drift terms.  Note the options are different than for \parlink{thetaDerivativeScheme}
and \parlink{zetaDerivativeScheme}.\\

{\ttfamily ExBDerivativeScheme} = 0: Use same differentiation matrices as for the parallel streaming term.  This option is best except for very
large radial electric fields, when the electric field is as large as the resonance or larger.\\

{\ttfamily ExBDerivativeScheme} = 1: Treat the $\vect{E}\times\vect{B}$ drift terms using a 4 point upwinded stencil (1 point on 1 side, 2 points on the other.)
}
